---
title: "Predicting attitudes towards racist college professors"
author: "Maria Benavides"
date: "`r lubridate::today()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(broom)
library(kableExtra)
library(jtools)
theme_set(new = theme_minimal())

prof_data <- rcfss::gss_colrac
```

## Introduction 

Using data from the General Social Survey (GSS) – which provides information about what Americans think and feel about issues of national spending priorities, crime and punishment, intergroup relations, and confidence in institutions – we will analyze the factors that determine whether or not an individual believes a racist person should be allowed to teach.

**Table 1** shows whether age, gender, level of education and political party identification have incidence in a person’s attitude towards a racist professor teaching in a college or university. 


```{r model 1, echo=FALSE, message=FALSE}
model_1 <- glm(colrac ~ age + degree + partyid_3 + sex, data=prof_data, family = "binomial")
regr_model1 <- tidy(model_1) %>%
  rename(
    "Predictor" = term,
    "B" = estimate, 
    "SE" = std.error, 
    "t" = statistic, 
    "p" = p.value
    ) 
kable(regr_model1, 
      digits = 3, 
      caption = "Table 1: predictors of attitudes towards racist college professors"
      ) 
```

According to this model: 

* The older a person is, the lower the probability of accepting that a racist person should be allowed to teach. 
* People with higher levels of education are more likely to accept that a racist person should be allowed to teach, relatively to a person with no high school diploma. 
* Republicans and independents are more likely to accept that a racist person should be allowed to teach, relatively to a democrat. 
* Women are less likely to accept that a racist person should be allowed to teach, relatively to men. 

The following graph presents this same information. 


```{r plot model 1, echo=FALSE}

# Plot linear regression 
plot_summs(model_1) +
  labs(title="Graph 1: predictors of attitudes towards racist college professors") 

```



## Session info

```{r}
devtools::session_info()
```
