---
title: "Predicting attitudes towards racist college professors"
author: "Maria Benavides"
date: "`r lubridate::today()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(broom)
library(kableExtra)
library(jtools)
theme_set(new = theme_minimal())

prof_data <- rcfss::gss_colrac
```

## Introduction 

Using data from the General Social Survey (GSS) – which provides information about what Americans think and feel about issues of national spending priorities, crime and punishment, intergroup relations, and confidence in institutions – we will analyze the factors that determine whether or not an individual believes a racist person should be allowed to teach.


### First approach: considering socio-demographic variables 

**Table 1** shows whether age, gender, level of education and political party identification have incidence in a person’s attitude towards a racist professor teaching in a college or university. 


```{r model 1, echo=FALSE, message=FALSE}
model_1 <- glm(colrac ~ age + degree + partyid_3 + sex, data=prof_data, family = "binomial")
regr_model1 <- tidy(model_1) %>%
  rename(
    "Predictor" = term,
    "B" = estimate, 
    "SE" = std.error, 
    "t" = statistic, 
    "p" = p.value
    ) 
kable(regr_model1, 
      digits = 3, 
      caption = "Table 1: predictors of attitudes towards racist professors"
      ) 
```

According to this model: 

* The older a person is, the lower the probability of accepting that a racist person should be allowed to teach. 
* People with higher levels of education are more likely to accept that a racist person should be allowed to teach, relatively to a person with no high school diploma. 
* Republicans and independents are more likely to accept that a racist person should be allowed to teach, relatively to a democrat. 
* Women are less likely to accept that a racist person should be allowed to teach, relatively to men. 

When including a dummy variable indicating **whether the surveyed person is black or whether is hispanic**, most of the results remain the same; only the factor regarding  a person's identification with the Republican party loses statistical significance. In addition, we can state that African Americans and Hispanic people are less likely to accept that a racist professor teaches at a university. This is shown in **Table 2**.


```{r model 2, echo=FALSE, message=FALSE}

model_2 <- glm(colrac ~ age + degree + partyid_3 + sex + black + hispanic_2, data=prof_data, family = "binomial")
regr_model2 <- tidy(model_2) %>%
  rename(
    "Predictor" = term,
    "B" = estimate, 
    "SE" = std.error, 
    "t" = statistic, 
    "p" = p.value
    ) 
kable(regr_model2, 
      digits = 3, 
      caption = "Table 2: predictors of attitudes towards racist professors considering race"
      ) 

```


### Second approach: considering scales

Now, we should consider that other factors influence the attitudes of people towards racism; we can examine authoritarian, egalitarian and tolerance tendency, and understand how influential they are in the level of racism acceptence.

```{r model scales, echo=FALSE, message=FALSE}
model_3 <- glm(colrac ~ authoritarianism + egalit_scale + tolerance, data=prof_data, family = "binomial")
regr_model_scale <- tidy(model_3) %>%
  rename(
    "Predictor" = term,
    "B" = estimate, 
    "SE" = std.error, 
    "t" = statistic, 
    "p" = p.value
    ) 
kable(regr_model_scale, 
      digits = 3, 
      caption = "Table 3: scales as predictors of attitudes towards racist professors"
      ) 
```

According to **Table 3**, as we could, a prior, assume, people with higher tendency levels of tolerance, are more acceptance of racist behaviors; that is, they would be more likely to accept that that a racist person should be allowed to teach. Also, more authoritarian people present the same behavior. Mine while, those who are more egalitarian, are less likely to accept that a racist professor teaches at a university or college. 

```{r plot model 1 & 2 & 3, echo=FALSE, message=FALSE}

# Plot linear regression 
plot_summs(model_1, model_2, model_3) +
  labs(title="Predictors of attitudes towards racist professors") 

```

## Conclusions

Based on the previous analysis, we could argue that many factors influence people’s attitudes towards racism. In general terms we could say that: 

* Being part of a minority group decreases the probability of accepting racist behaviors. 
* Political affiliations are also correlated with the level of acceptance of racism. A republican person is more likely to tolerate the fact that a racist professor teaches at a university. 
* Identifying as women is negatively correlated with the likelihood of accepting a racist professor. 
* People with higher levels of tolerance, are also more accepting of racist professors teaching in universities and colleges. 


## Session info

```{r}
devtools::session_info()
```
