---
title: "President Donald Trump"
author: "Maria Benavides"
date: "`r lubridate::today()`"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(here)
library(broom)
library(kableExtra)

theme_set(new = theme_minimal())
```


```{r import data, message = FALSE}
# Import data 
trump_survey <- read_csv(here("data/trump.csv"))
```

## Part 1: Donald Trump 

### Q1: linear regression model of the relationship between the importance of the video and feelings towards Donald Trump

```{r linear regression, message = FALSE}
# Run a bivariate linear regression 
video_incidence <- lm(trump ~ video, data=trump_survey)
regression_tbl <- tidy(video_incidence) %>%
  rename(
    "Predictor" = term,
    "B" = estimate, 
    "SE" = std.error, 
    "t" = statistic, 
    "p" = p.value
    ) %>%
kable(digits = 3, 
      caption = "Table 1: relationship between importance of video and feelings towards Donald Trump") 



# Plot a bivariate linear regression 

ggplot(trump_survey, aes(x=video, y=trump)) + 
  geom_point() +
  geom_smooth(method=lm) +
  labs(title="Graph 1: correlation between video and attitudes torwars Trump", 
       x="Video importance", 
       y="Attitude towards Donald Trump")

```

As both table 1 and graph 1 show, there is a negative strong correlation between the importance surveyd people attributed to the video and feelings towards Donald Trump; that is to say, the greater the video importance the colder the feelings towards Trump. 

### Q2: linear regression model of the relationship between the importance of the video and feelings towards Donald Trump, given the avaiblable variables

```{r linear regression and variables, message = FALSE}

# Run a linear regression considering all regressions and interacting age and party identification
video_incidence_all <- lm(trump ~ video + female + pid + age + educ + pid * age, data=trump_survey)
regression_tbl_all <- tidy(video_incidence_all) %>%
  rename(
    "Coefficient" = estimate, 
    "Standard Error" = std.error, 
    "T-value" = statistic, 
    "P-value" = p.value
    )
kable(regression_tbl_all, digits = 3, caption = "Table 2: variables influencing feelings towards Donald Trump") 

# Plot a bivariate linear regression 

ggplot(trump_survey, aes(x=video, y=trump)) + 
  geom_point() +
  geom_smooth(method=lm) +
  labs(title="Graph 1: correlation between video and attitudes torwars Trump", 
       x="Video importance", 
       y="Attitude towards Donald Trump")


```


## Session info

```{r}
devtools::session_info()
```
