---
title: "President Donald Trump"
author: "Maria Benavides"
date: "`r lubridate::today()`"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(here)
library(broom)
library(kableExtra)

theme_set(new = theme_minimal())
```


```{r import data, message = FALSE}
# Import data 
trump_survey <- read_csv(here("data/trump.csv"))
```

## Part 1: linear regression model of the relationship between the importance of the video and feelings towards Donald Trump

```{r linear regression, message = FALSE}
# Run a bivariate linear regression 
video_incidence <- lm(trump ~ video, data=trump_survey)
regression_tbl <- tidy(video_incidence) %>%
  rename(
    "Coefficient" = estimate, 
    "Standard Error" = std.error, 
    "T-value" = statistic, 
    "P-value" = p.value
    )
kable(regression_tbl, digits = 3, caption = "Table 1: relationship between the importance of the video and feelings towards Donald Trump") 

# Plot a bivariate linear regression 

ggplot(trump_survey, aes(x=video, y=trump)) + 
  geom_point() +
  geom_smooth(method=lm) +
  labs(title="Graph 1: correlation between video and attitudes torwars Trump", 
       x="Video importance", 
       y="Attitude towards Donald Trump")

```

As both table 1 and graph 1 show, there is a negative strong correlation between the importance surveyd people attributed to the video and feelings towards Donald Trump; that is to say, the greater the video importance the colder the feelings towards Trump. 

## Session info

```{r}
devtools::session_info()
```
